%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For technical support please email: ykoh@wspc.com.sg (or) rajesh@wspc.com.sg %%
%% The content, structure, format and layout of this style file is the          %%
%% property of World Scientific Publishing Co. Pte. Ltd.                        %%
%% Copyright 2014 by World Scientific Publishing Co.                            %%
%% All rights are reserved.                                                     %%
%%                                                                              %%
%% Proceedings Trim Size: 9in x 6in                                             %%
%% Text Area: 7.35in (include runningheads) x 4.5in                             %%
%% Main Text is 10/13pt                                                         %%
%% Last Modified: 24-01-2014                                                    %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\documentclass[wsdraft]{ws-procs9x6}  % to draw border line around text area
%\documentclass[wssquare]{ws-procs9x6} % for citations in square brackets (consult your editor before picking up this style)
\documentclass{ws-procs9x6}            % default, citations in superscript
\usepackage{lmodern}

\begin{document}

\title{Recommender systems with heterogeneous information network for cold-start items}

\author{Di Zhang, Qian Zhang, Guanquan Zhang, Jie Lu}

\address{\textit{Decision Systems and e-Service Intelligence Laboratory,} \\
\textit{Centre for Artificial Intelligence}\\
University of Technology Sydney, Australia \\
Di.Zhang-7@student.uts.edu.au, Qian.Zhang-1@uts.edu.au \\
Guangquan.Zhang@uts.edu.au, Jie.Lu@uts.edu.au}

\begin{abstract}
Recommender System is a widely adopted research topic in real-world applications. Collaborative Filtering (CF) and Matrix based approach has been the main stream methodology for the past decade in both implicit and explicit recommendation tasks. One challenge most of above methods having is "Cold Start" problem, that is when newly emerged data set has little or no available interactions for training. Some model based CF condense user/item data into latent space, through learning process such as Factorization Machine. However, in case of constant cold start problem, those approach can be ineffective and costly. In this paper, we propose MERec, a novel approach that adopts graph meta-path embedding to learns item/user features independently besides learning user-item interactions. It allows unseen data points to be incorporated as part of user/item learning process, hence effectively reduce the impact in cold start problem for new or sparse dataset.
\end{abstract}

\keywords{recommender system; cold-start; heterogeneous information network.}

\bodymatter

\input{section_1_introduction.tex}

\input{section_2_background.tex}

\input{section_3_methods.tex}

\input{section_4_experiment.tex}

\input{section_5_conclusion.tex}



% Unnumbered appendix sections can be obtained using \verb|\section*|.
% \section*{Acknowledgment}

% The preferred spelling of the word ``acknowledgment'' in America is without 
% an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
% G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
% acknowledgments in the unnumbered footnote on the first page.

\bibliographystyle{ws-procs9x6} % for numbered citation & references
\bibliography{ref}

\end{document}

\end{document}